\documentclass[10pt,a4paper]{article}

\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}
\usepackage[hidelinks]{hyperref}
\usepackage{xparse}

\usepackage[utf8]{inputenc}
\inputencoding{utf8}
\usepackage[official]{eurosym}

\usepackage[
	top=0.75cm,
	bottom=0.75cm,
	left=0.75cm,
	right=0.75cm,
]{geometry}

\begin{document}
	\pagenumbering{gobble}
	\clearpage

	\vspace{-6px}
	\noindent\fbox{
		\begin{minipage}[t]{0.425\textwidth}
			\vspace{2px}
			\begin{minipage}[t]{0.21\textwidth}
				{\Huge I AM}
			\end{minipage}
			\hskip -0.25em
			\begin{minipage}[t]{0.79\textwidth}
				\vskip -1.9em
				{
				\begin{tabular}{l}
					RWTH STUDENT {\footnotesize AND}\\ GEORGIA TECH ALUMNI
				\end{tabular}
				}
			\end{minipage}\\[2px]
			{STUDYING COMPUTER SCIENCE} {\footnotesize AND MATH}\\[5px]
			{\Huge DAVID STUTZ}\\[2px]
			{COMPUTER VISION RESEARCH SCIENTIST}
			%{COMPUTER VISION} {RESEARCH SCIENTIST}%\\[2px]
			%{WEB DEVELOPER}
			\vspace{2px}
		\end{minipage}
	}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.26\textwidth}
		\vspace{2px}
		{\LARGE CURRENTLY}\\[6px]
		RWTH Aachen University\\
		M.Sc. in Computer Science
		\vskip 4px
		MOBIS Parts Europe N.V.\\
		Front Camera Intern
	\end{minipage}
	\begin{minipage}[t]{0.215\textwidth}
		\vspace{2px}
		{\LARGE CONTACT}\\[6px]
		davidstutz@web.de
		\vskip 4px
		\href{http://davidstutz.de}{davidstutz.de}\\
		\href{https://github.com/davidstutz}{github.com/davidstutz}\\
		%\href{https://www.xing.com/profile/David_Stutz5}{xing.to/DavidStutz}\\
		\href{https://www.linkedin.com/in/davidstutz92}{de.linkedin.com/in/davidstutz92}
	\end{minipage}
	\vskip 6px
	\noindent\fbox{
		\begin{minipage}{0.975\textwidth}
			\vspace{4px}
			I am passionate about computer science -- its versability, its origins in mathematics, its applications. Focusing on computer vision and machine learning, I combine the depth of theory with the most interesting applications of todays world.
			\vspace{2px}
		\end{minipage}
	}
	\vskip 10px
	\noindent\begin{minipage}[t]{0.435\textwidth}
		\noindent{\LARGE EDUCATION}\\[6px]
		RWTH Aachen University\\
		M.Sc. in Computer Science (expected 2017, GPA: 1.0)\\
		B.Sc. in Computer Science (with distinction, GPA: 1.1)\\
		%{\footnotesize \textit{Minor: Mathematics}}\\
		{\footnotesize \textit{Coursework: Computer Vision, Machine Learning, Data Mining, Numerical Analysis, Convex Optimization, Mathematical Image processing, Data Science, Complexity Theory}}\\
		{\footnotesize \textit{MOOCs: Linear and Integer Programming, Social Network Analysis, Game Theory, Cryptography, Introduction to Finance, Introduction to Operations Management}}\\
		{\footnotesize \textit{Thesis: Superpixel Segmentation using Depth Information.}}\\
		{\footnotesize \textit{Advisor: Prof. Dr. Bastian Leibe}}\\
		\hphantom{a}\hfill{\scriptsize 10/2011 -- today, Aachen, GER}
		\vskip 4px
		\noindent Georgia Institute of Technology\\
		Graduate Exchange Student (GPA: 4.0)\\
		{\footnotesize \textit{Coursework: Statistical Techniques in Robotics, Probabilistic Graphical Models, Special Problems in Computer Vision}}\\
		{\footnotesize \textit{Advisor: Prof. Irfan Essa, Ph.D.}}\\
		\hphantom{a}\hfill{\scriptsize 01/2015 -- 05/2015, Atlanta, GA}
		\vskip 12px
		
		{\LARGE AWARDS}\\[6px]
		Accenture Future Technology Leaders {\scriptsize 2015 -- today}\\
		{\footnotesize Development program including workshops, networking events and individual mentoring awarded to excellent STEM students.}\\
		Hans Hermann-Voss Scholarship {\scriptsize 2015}\\
		{\footnotesize Study abroad scholarship worth \euro{1800} awarded for excellent grades.}\\
		Germany Scholarship {\scriptsize 2014 -- today}\\
		{\footnotesize Scholarship worth \euro{3600}/year awarded for excellent grades.}\\
		RWTH Aachen University Dean's List {\scriptsize 2012, 2013, 2014}\\
		{\footnotesize Awarded to the top 5\% in each discipline.}\\
		% Selection Seminar of the German National Academic Foundation {\scriptsize 2013}\\
		careerloft.de Online Scholarship {\scriptsize 2012 -- today}\\
		e-fellows.net Online Scholarship {\scriptsize 2011 -- today}
		%German Physical Society Book Price {\scriptsize 2011}\\
		%German Junior Academy {\scriptsize  2005}
		\vskip 12px
		
		\noindent{\LARGE PROJECTS {\footnotesize on \href{https://github.com/davidstutz}{github.com/davidstutz}}}\\[6px]
		SEEDS Revised and Superpixels Revisited\\
		{\footnotesize\textit{Efficient implementation of SEEDS superpixels bundled with recent superpixel algorithms including an extended version of the Berkeley Segmentation Benchmark for evaluation.}}
		\vskip 4px
		Graph-Based Hierarchical Video Segmentation\\
		{\footnotesize\textit{Efficient implementation of graph-based hierarchical image and video segmentation.}}
		\vskip 4px
		iPiano: Non-Convex and Non-Smooth Optimization\\
		{\footnotesize\textit{Implementation of iPiano for non-convex and non-smooth optimization by combining forward-backward splitting with an inertial force.}}
		\vskip 4px
		%More projects at \href{https://github.com/davidstutz}{github.com/davidstutz}.
		Various Twitter Bootstrap, Wordpress, Kohana and CMSimple Plugins\\
		
		\footnotetext{{\scriptsize Grades are given in their original grading system.}}
		\footnotetext{{\scriptsize Documents proving the above claims are given upon request.}}
		\footnotetext{{\scriptsize Last updated: \today.}}
	\end{minipage}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.525\textwidth}
		\noindent{\LARGE PUBLICATIONS}\\[6px]
		Stutz, D.: Superpixel Segmentation: An Evaluation. In: German Conference on Pattern Recognition (GCPR), 2015.
		\vskip 12px
		
		\noindent{\LARGE EXPERIENCE}\\[6px]
		MOBIS Parts Europe N.V.\\
		Front Camera Intern\\
		%{\footnotesize Advisor: Dr. Thomas Guthier}\\
		%{\footnotesize\textit{Skills: C++ (Caffe, OpenCV, Boost, CMake), Python (NumPy, Jupyter)}}\\
		\hphantom{a}\hfill{\scriptsize 04/2016 -- today, Frankfurt (a.M.), GER}
		\vskip 4px
		
		Computer Vision Group, RWTH Aachen University\\
		Student Research Assistant, Computer Vision\\
		{\footnotesize\textit{Evaluation and comparison of state-of-the-art superpixel algorithms.}}\\
		%{\footnotesize Advisor: Prof. Dr. Bastian Leibe}
		%{\footnotesize\textit{Skills: C++ (OpenCV, Boost, CMake), MatLab, LaTeX (TikZ, PGFPlots), Mercurial}}\\
		%{\footnotesize\textit{Advisor: Prof. Dr. Bastian Leibe}}\\
		\hphantom{a}\hfill{\scriptsize 05/2015 -- 03/2016, Aachen, GER}
		\vskip 4px
		Fyusion Inc.\\
		Research Scientist, Computer Vision\\
		%{\footnotesize Advisors: Dr. Stefan Holzer; Alexander Trevor, Ph.D.}\\
		%{\footnotesize\textit{Skills: C++ (OpenCV, Boost, CMake), MatLab, LaTeX, Git}}\\
		\hphantom{a}\hfill{\scriptsize 05/2015 -- 03/2016, San Francisco, CA}
		\vskip 4px
		Computational Perception Lab, Georgia Institute of Technology\\
		Visiting Graduate Student\\
		{\footnotesize \textit{Video segmentation using intrinsic characteristics and semantic segmentation of weakly-labeled video.}}\\
		%{\footnotesize Advisor: Prof. Irfan Essa, Ph.D.}\\
		%{\footnotesize\textit{Skills: C++ (OpenCV, Boost, CMake), MatLab, Mercurial}}\\
		%{\footnotesize \textit{Advisor: Prof. Irfan Essa, Ph.D.}}\\
		\hphantom{a}\hfill{\scriptsize 01/2015 -- 05/2015, Atlanta, GA}
		\vskip 4px
		MATHCCES, RWTH Aachen University\\
		Tutor\\
		{\footnotesize\textit{``Fundamentals of Mathematics II'', ``Calculus for Computer Science''}}\\
		{\footnotesize\textit{Responsibilities include presenting exercises to a group of 30-50 students and grading weekly homework as well as final exams.}}\\
		\hphantom{a}\hfill{\scriptsize 10/2013 -- 01/2014, 04/2014 -- 09/2014, Aachen, GER}
		\vskip 4px
		RS Computer\\
		Web Developer\\
		{\footnotesize\textit{Development of themes and plugins for CMSimple and Wordpress; and conception, development as well as maintenance of individual web applications for medium-sized companies.}}\\
		%{\footnotesize\textit{Skills: PHP (Kohana, Wordpress, xtCommerce, CMSimple), JavaScript (jQuery), SQL (MySQL), HTML/CSS (Twitter Bootstrap), Mercurial}}\\
		\hphantom{a}\hfill{\scriptsize 01/2009 -- 03/2014, 10/2014 -- 04/2015, Sinzig, GER}
		\vskip 4px
		%Fraunhofer Institute for Communication, Information Processing and Ergonomics\\
		Fraunhofer FKIE\\
		Student Employee\\
		{\footnotesize\textit{Introduction to C++ and 3D modeling using Blender; development of an interactive web application based on PHP and JavaScript for complex database queries based on SQL; plugin development for Piwik; and data visualization using d3.js.}}\\
		%{\footnotesize\textit{Skills: C++, PHP (Kohana, Piwik), JavaScript (jQuery, d3.js), SQL (MySQL), HTML/CSS}}\\
		%{\footnotesize\textit{Advisor: Dr. Carsten Winkelholz}}\\
		\hphantom{a}\hfill{\scriptsize 10/2009, 05/2011 -- 07/2011, 03/2012, 08/2012 -- 09/2012, Wachtberg, GER}
		\vskip 12px
		
		%\noindent{\LARGE COURSEWORK}\\[6px]
		%Computer Vision 1 \& 2, Machine Learning, Data Mining Algorithms 1 \& 2, Statistical Techniques in Robotics, Probabilistic Graphical Models, Numerical Analysis 1 \& 2, Convex Optimization, Mathematical Image Processing 1 \& 2, Foundations of Data Science, Complexity Theory
		%\vskip 12px
		
		\noindent{\LARGE SKILLS}\\[6px]
		C/C++ (OpenCV), MatLab, PHP, JavaScript (jQuery, d3.js), HTML/CSS (Twitter Bootstrap), SQL, LaTeX (PGFPlots, TikZ), Git, Mercurial
	\end{minipage}
\end{document}