\documentclass[11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{lipsum}
\usepackage{hyperref}
\usepackage{hanging}
\usepackage{changepage}

% \usepackage[scaled]{helvet} % Helvetica
\usepackage[scaled]{uarial} % Arial
\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is sans serif
\usepackage[T1]{fontenc}

\newenvironment{bottompar}{\par\vspace*{\fill}}{\clearpage}
\newcommand{\indentwidth}{0.08\textwidth}

\usepackage[
top = 2.25cm,
bottom = 2.25cm,
left = 3.5cm,
right = 3.5cm,
textwidth = 13.5cm]{geometry}

\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\setlength{\headsep}{0pt}
\setlength{\topskip}{0pt}
\setlength{\topmargin}{0pt}
\setlength{\topsep}{0pt}
\setlength{\partopsep}{0pt}

\usepackage[compact]{titlesec}
\titlespacing*{\section} {0pt}{2ex plus 1ex minus .2ex}{2ex plus .2ex}
\titlespacing*{\subsection} {0pt}{1.75ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\begin{document}
\thispagestyle{empty}

\titleformat{\section}[block]{\normalfont\LARGE\bfseries\filcenter}{}{}{}
\section*{David Stutz}

\titleformat{\section}
{\normalfont\Large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}
{\normalfont\large\bfseries}{\thesubsection}{1em}{}

\begin{center}
\href{mailto:davidstutz@web.de}{davidstutz@web.de} \quad \hyperlink{davidstutz.de}{http://davidstutz.de}
\end{center}

\section*{Profile}

Inspired by the elegant and simultaneously versatile world of computer science, I am a student eager to learn more in all its different disciplines. I focus on computer vision and machine learning -- combining the depth of theory with the most interesting applications of today's world.
\vskip 0.5ex

%\noindent Planning a career in academia, I am not only eager to acquiring new knowledge, but also motivated to share this knowledge with other professionals as well as future generations.

\section*{Academic Training}

\hangpara{\indentwidth}{1}\textbf{RWTH Aachen University}, Aachen, Germany, 2011 -- present

\hangpara{\indentwidth}{1}Master of Science in Computer Science, expected September 2016

\hangpara{\indentwidth}{1}Bachelor of Science in Computer Science, with Distinction (4.0 GPA), October 2014\\
Advisor: Prof. Dr. Bastian Leibe\\
\textit{Superpixel Segmentation using Depth Information.}
%Focus: Computer Vision, Machine Learning, Data Mining\\
%Minor: Mathematics, in particular Numerical Analysis

\hangpara{\indentwidth}{1}\textbf{Georgia Institute of Technology}, Atlanta, GA, January 2015 -- May 2015

\hangpara{\indentwidth}{1}Graduate Exchange in Computer Science  (4.0 GPA, Hans Hermann-Voss Scholarship)

\hangpara{\indentwidth}{1}\textbf{Gymnasium Calvarienberg}, Ahrweiler, Germany, 2002 -- 2011\\
Abitur (Very Good, A)\\
Majors: Physics, Mathematics, English, Geography

\subsection*{Awards and Scholarships}

% \hangpara{\indentwidth}{1}Hans Hermann-Voss Scholarship, 2015

\hangpara{\indentwidth}{1}RWTH Aachen University Dean's List, 2014

\hangpara{\indentwidth}{1}RWTH Aachen University Education Fund (Germany Scholarship), 2014 -- present

\hangpara{\indentwidth}{1}RWTH Aachen University Dean's List, 2013

\hangpara{\indentwidth}{1}Participation in the Selection Seminar of the German National Academic Foundation, 2013

\hangpara{\indentwidth}{1}RWTH Aachen University Dean's List, 2012

\hangpara{\indentwidth}{1}careerloft.de Scholarship, October 2012 -- present

\hangpara{\indentwidth}{1}e-fellows.net Scholarship, May 2011 -- present

\hangpara{\indentwidth}{1}German Physical Society Book Prize for Outstanding Merits in Physics, 2011

\hangpara{\indentwidth}{1}German Junior Academy for the Promotion of Young Talents, 2005

\section*{Research Experience}

\hangpara{\indentwidth}{1}Visiting Graduate Student, Computational Perception Laboratory, Georgia Institute of Technology, Atlanta, GA, January 2015 -- May 2015\\
Advisor: Prof. Irfan Essa, Ph.D.\\
\textit{Video segmentation using intrinsic characteristics.}

\section*{Teaching Experience}

\hangpara{\indentwidth}{1}Tutor, ``Fundamentals of Mathematics II'', MATHCCES, RWTH Aachen University, Aachen, Germany, April 2014 -- September 2014\\
\textit{Responsibilities include presenting exercises to a group of 30 students and grading weekly homework.}

\hangpara{\indentwidth}{1}Tutor, ``Calculus for Students of Computer Science'', MATHCCES, RWTH Aachen University, Aachen, Germany, October 2013 -- March 2014\\
\textit{Responsibilities include presenting exercises to a group of  50 students and grading weekly homework as well as the final exam.}

% "Fit für die Lehre in der Mathematik":
%\hangpara{\indentwidth}{1}Preparation Seminar on Teaching Mathematics, RWTH Aachen University, Germany, October 2013

\section*{Work Experience}

\hangpara{\indentwidth}{1}Web Developer, RS Computer, Sinzig, Germany, January 2009 -- March 2014, October 2014 -- present\\
\textit{Development of a Content Management System including theme and plugin development for Wordpress, CMSimple and xtCommerce. Design, development and maintenance of individual software for medium-sized companies.}

\hangpara{\indentwidth}{1}Student Employee, Fraunhofer Institute for Communication, Information Processing and Ergonomics, Wachtberg, Germany, August 2012 -- September 2012\\
\textit{Data visualization using JavaScript and d3.js.}

\hangpara{\indentwidth}{1}Student Employee, Fraunhofer Institute for Communication, Information Processing and Ergonomics, Wachtberg, Germany, March 2012\\
\textit{Plugin development for Piwik (Open Source Web Analytics).}

\hangpara{\indentwidth}{1}Student Employee, Fraunhofer Institute for Communication, Information Processing and Ergonomics, Wachtberg, Germany, May 2011 -- July 2011\\
\textit{Web development using PHP and Javascript based on a HMVC framework including a database connection to a MySQL database.}

\hangpara{\indentwidth}{1}Intern, Fraunhofer Institute for Communication, Information Processing and Ergonomics FKIE, Wachtberg, Germany, October 2009\\
\textit{Introduction to C++ and 3D modeling using Blender.}

\section*{Service and Memberships}

\hangpara{\indentwidth}{1}Student Member, German Informatics Society, Germany, 2014 -- present

\hangpara{\indentwidth}{1}Volunteer, Conference on Software Engineering, Aachen, Germany, 2013

\hangpara{\indentwidth}{1}Member, Society of Friends of the Saarland Mandolin Orchestras, Germany, 2013 -- present

\hangpara{\indentwidth}{1}Member, Saarland Mandolin Orchestra, Germany, 2012 -- present

\hangpara{\indentwidth}{1}Member, German Plucked String Federation, Germany, 2012 -- present

\hangpara{\indentwidth}{1}Guitar Teacher, Music School Steps on Stage, Sinzig, Germany, 2011

\hangpara{\indentwidth}{1}Member, Saarland Mandolin Youth Orchestra, Germany, 2006 -- 2008

%\section*{Skills}

%Programming languages: C/C++, MatLab, PHP, JavaScript, HTML, SQL\\
%Tools and libraries: Git, Mercurial, OpenCV, d3.js, jQuery

\section*{Interests and Activities}

\hangpara{\indentwidth}{1}Classical and electrical guitar with 16 years of experience including several prizes from the music competition "Jugend musiziert" for classical guitar ensemble, several guitar and mandolin seminars arranged by the German Plucked String Federation, teaching experience, and memberships in various mandolin orchestras, 1998 -- present

\hangpara{\indentwidth}{1}Web development and open source including plugins and themes for the content management systems Wordpress and CMSimple, modules for the PHP framework Kohana as well as Twitter Bootstrap and jQuery plugins, 2009 -- present

\hangpara{\indentwidth}{1}Massive Open Online Courses including courses on cryptography, game theory, social network analysis, and linear and integer programming, 2012 -- present

\begin{bottompar}
\begin{center}
\hangpara{0cm}{1}\scriptsize{Documents proving the above claims are given on request.}
\end{center}
\end{bottompar}

\end{document}