\documentclass[10pt,a4paper]{article}

\renewcommand{\familydefault}{\sfdefault}
\usepackage{helvet}
\usepackage{hyperref}
\usepackage{xparse}

\usepackage[utf8]{inputenc}
\usepackage[
	top=0.5cm,
	bottom=0.75cm,
	left=0.75cm,
	right=0.75cm,
]{geometry}

\begin{document}
	\pagenumbering{gobble}
	\clearpage
	
	\begin{center}
		{\scriptsize Meant to be viewed on screen or printed on DIN A4 paper.}
	\end{center}
	\vspace{-6px}
	\noindent\fbox{
		\begin{minipage}[t]{0.425\textwidth}
			\vspace{2px}
			{\huge I AM} {\footnotesize OPENSOURCE FAN}\\[2px]
			{STUDYING COMPUTER SCIENCE} {\footnotesize AND MATH}\\[5px]
			{\Huge DAVID STUTZ}\\[2px]
			{RWTH STUDENT} {\footnotesize AND} {GEORGIA TECH ALUMNI}\\[2px]
			{COMPUTER VISION} {RESEARCH SCIENTIST}\\[2px]
			{WEB DEVELOPER}{\footnotesize, VIDEOGAME ENTHUSIAST, GUITARIST}
			\vspace{2px}
		\end{minipage}
	}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.3\textwidth}
		\vspace{2px}
		{\LARGE CURRENTLY}\\[6px]
		RWTH Aachen University\\
		M.Sc. in Computer Science\\
		\hphantom{a}\hfill{\scriptsize 10/2014 -- today, Aachen, GER}
		\vskip 4px
		RWTH Aachen University\\
		Student Research Assistant\\
		\hphantom{a}\hfill{\scriptsize 05/2015 -- today, Aachen, GER}
	\end{minipage}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.175\textwidth}
		\vspace{2px}
		{\LARGE CONTACT}\\[6px]
		davidstutz@web.de
		\vskip 4px
		\href{http://davidstutz.de}{davidstutz.de}\\
		\href{https://github.com/davidstutz}{github.com/davidstutz}\\
		\href{https://twitter.com/david_stutz}{twitter.com/david\_stutz}
	\end{minipage}
	\vskip 6px
	\noindent\fbox{
		\begin{minipage}{0.975\textwidth}
			\vspace{2px}
			I am passionate about computer science -- its versatility, its origins in mathematics, its applications. Focusing on computer vision and machine learning, I combine the depth of theory with the most interesting applications of today's world.
			\vskip 4px
			Planning a career in academia, I am not only eager to acquire new knowledge, but also motivated to share this knowledge with other professionals as well as future generations.
		\end{minipage}
	}
	\vskip 10px
	\noindent\begin{minipage}[t]{0.55\textwidth}
		\noindent{\LARGE EDUCATION}\\[6px]
		RWTH Aachen University\\
		M.Sc. in Computer Science (expected 2016, 4.0 GPA)\\
		B.Sc. in Computer Science (with distinction, 4.0 GPA)\\
		%{\small \textit{Minor: Mathematics}}\\
		{\small \textit{Thesis: Superpixel Segmentation using Depth Information.${}^\ast$}}\\
		{\small \textit{Advisor: Prof. Dr. Bastian Leibe}}\\
		\hphantom{a}\hfill{\scriptsize 10/2011 -- today, Aachen, GER}
		\vskip 4px
		\noindent Georgia Institute of Technology\\
		Graduate Exchange Student (4.0 GPA)\\
		\hphantom{a}\hfill{\scriptsize 01/2015 -- 05/2015, Atlanta, GA}
		\vskip 12px
		
		\noindent{\LARGE EXPERIENCE}\\[6px]
		Computer Vision Group, RWTH Aachen University\\
		Student Research Assistant\\
		{\small\textit{Evaluation and comparison of state-of-the-art superpixel algorithms.}}\\
		{\small\textit{Advisor: Prof. Dr. Bastian Leibe}}\\
		\hphantom{a}\hfill{\scriptsize 05/2015 -- today, Aachen, GER}
		\vskip 4px
		Computational Perception Laboratory, Georgia Institute of Technology\\
		Visiting Graduate Student\\
		{\small \textit{Video segmentation using intrinsic characteristics and semantic segmentation of weakly-labeled video.}}\\
		{\small \textit{Advisor: Prof. Irfan Essa, Ph.D.}}\\
		\hphantom{a}\hfill{\scriptsize 01/2015 -- 05/2015, Atlanta, GA}
		\vskip 4px
		MATHCCES, RWTH Aachen University\\
		Tutor, {\small\textit{``Fundamentals of Mathematics II'', ``Calculus for Computer Science''}}\\
		{\small\textit{Responsibilities include presenting exercises to a group of 30-50 students and grading weekly homework as well as final exams.}}\\
		\hphantom{a}\hfill{\scriptsize 10/2013 -- 01/2014, 04/2014 -- 09/2014, Aachen, GER}
		\vskip 4px
		RS Computer\\
		Web Developer\\
		{\small\textit{Development of themes and plugins for CMSimple and Wordpress; and conception, development as well as maintenance of individual web applications for medium-sized companies.}}\\
		\hphantom{a}\hfill{\scriptsize 01/2009 -- 03/2014, 10/2014 -- 04/2015, Sinzig, GER}
		\vskip 4px
		%Fraunhofer Institute for Communication, Information Processing and Ergonomics\\
		Fraunhofer FKIE\\
		Student Employee\\
		{\small\textit{Introduction to C++ and 3D modeling using Blender; development of an interactive web application based on PHP and JavaScript for complex database queries using SQL; plugin development for Piwik; and data visualization using d3.js.}}\\
		{\small\textit{Advisor: Dr. Carsten Winkelholz, Francois Kruger}}\\
		\hphantom{a}\hfill{\scriptsize 10/2009, 05/2011 -- 07/2011, 03/2012, 08/2012 -- 09/2012, Wachtberg, GER}
		\footnotetext{{\scriptsize ${}^\ast$ \label{footnote}Bachelor thesis and additional source code available at \href{https://github.com/davidstutz}{github.com/davidstutz}.}}
		\footnotetext{{\scriptsize Documents proving the above claims are given upon request.}}
	\end{minipage}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.4\textwidth}
		{\LARGE AWARDS}\\[6px]
		Accenture Future Technology Leaders Program {\scriptsize 2015}\\
		Hans Hermann-Voss Scholarship {\scriptsize 2015}\\
		Germany Scholarship {\scriptsize 2014 -- today}\\
		RWTH Aachen University Dean's List {\scriptsize 2012, 2013, 2014}\\
		% Selection Seminar of the German National Academic Foundation {\scriptsize 2013}\\
		careerloft.de Scholarship {\scriptsize 2012 -- today}\\
		e-fellows.net Scholarship {\scriptsize 2011 -- today}\\
		German Physical Society Book Price {\scriptsize 2011}\\
		German Junior Academy {\scriptsize  2005}
		\vskip 8px
		
		\noindent{\LARGE COURSEWORK${}^\ast$}\\[6px]
		Computer Vision, Computer Vision 2, Machine Learning, Data Mining Algorithms, Statistical Techniques in Robotics, Probabilistic Graphical Models, Numerical Analysis, Numerical Analysis 2, Complexity Theory
		\vskip 12px
		
		\noindent{\LARGE MOOCS}\\[6px]
		Linear and Integer Programming, Social Network Analysis, Game Theory, Cryptography, Introduction to Finance, Introduction to Operations Management
		\vskip 12px
		
		\noindent{\LARGE PROJECTS${}^\ast$}\\[6px]
		SEEDS Revised and Superpixels Revisited\\
		{\small\textit{Efficient implementation of SEEDS superpixels bundled together with recent superpixel algorithms including an extended version of the Berkeley Segmentation Benchmark for evaluation.}}
		\vskip 4px
		Bootstrap Multiselect and Strength Meter\\
		{\small\textit{Twitter Bootstrap plugins for user-friendly select elements and password inputs.}}
		\vskip 4px
		CMSimple News, Pictures and YouTube\\
		{\small\textit{CMSimple plugins for blogging and news articles, image galleries and sliders as well as YouTube video galleries.}}
		\vskip 4px
		Kohana Red, Green, Blue, Yellow and Gaps\\
		{\small\textit{Kohana plugins for authentication, access control and form generation and validation.}}
		\vskip 12px
		
		\noindent{\LARGE SKILLS}\\[6px]
		C/C++ (Boost, OpenCV, Point Cloud Library), MatLab, PHP, SQL, JavaScript (jQuery, d3.js), HTML, CSS/LESS, LaTeX (TikZ), Maple, Git, Subversion, Mercurial
	\end{minipage}
\end{document}