\documentclass[10pt,a4paper]{article}

\usepackage[defaultsans,scale=0.95]{cantarell}
\usepackage[T1]{fontenc}
%\renewcommand*{\rmdefault}{\fcafamily}

\usepackage[hidelinks]{hyperref}
\usepackage{xparse}

\usepackage[T1]{fontenc}
\usepackage[official]{eurosym}

\usepackage[usenames,dvipsnames]{xcolor}
\definecolor{darkgray}{HTML}{444444}
\definecolor{lightgray}{HTML}{666666}

% http://tex.stackexchange.com/questions/110362/how-can-i-make-footnote-text-color-match-body-text-color
\usepackage[flushmargin,hang]{footmisc} % http://stackoverflow.com/questions/2842722/how-do-i-control-footnotes-indentation-in-latex
\usepackage{bigfoot}
\def\footnotelayout{\color{lightgray}}

% http://tex.stackexchange.com/questions/21913/how-can-i-change-the-footnote-line-thickness-length
\renewcommand{\footnoterule}{%
  	\kern -3pt
	{\color{lightgray} \hrule width 2in}
	\kern 2.6pt
}

% http://tex.stackexchange.com/questions/121061/working-with-arial-or-helvetica-fonts
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault} 
\usepackage[T1]{fontenc}

% http://tex.stackexchange.com/questions/100731/omit-hanging-indent-in-bibtex
\usepackage{etoolbox}
\patchcmd{\thebibliography}
  {\advance\leftmargin\labelsep}
  {\leftmargin=0pt\itemindent=\labelwidth\advance\itemindent\labelsep}
  {}{}
  
\usepackage[
	top=1cm,
	bottom=0cm,
	left=1.25cm,
	right=1.25cm,
]{geometry}

% http://tex.stackexchange.com/questions/27843/level-of-boldness-changeable
\usepackage[outline]{contour}% http://ctan.org/pkg/contour
\contourlength{0.2pt}
\contournumber{1}

% http://tex.stackexchange.com/questions/27802/set-noindent-for-entire-file
\setlength\parindent{0pt}

\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\begin{document}
{\fcafamily
	\pagenumbering{gobble}
	\clearpage
	\hspace{-6px}\fcolorbox{lightgray}{white}{
	\begin{minipage}[t]{0.435\textwidth}
		\vspace{3px}
		\begin{minipage}[t]{0.22\textwidth}
			\vskip -12px
			{\Huge\color{darkgray}\textbf{I AM}}
		\end{minipage}
		\hskip -0.25em
		\begin{minipage}[t]{0.79\textwidth}
			%\vskip -2em
			\begin{tabular}{l}
				{\color{lightgray}RWTH STUDENT} {\footnotesize\color{lightgray} AND}\\ {\color{lightgray}GEORGIA TECH ALUMNI}
			\end{tabular}
		\end{minipage}\\[2px]
		{\color{lightgray}STUDYING COMPUTER SCIENCE} {\footnotesize\color{lightgray} AND} {\color{lightgray}MATH}\\[4px]
		{\Huge \textbf{{DAVID} STUTZ}}\\[2px]
		{\color{lightgray}COMPUTER VISION RESEARCH SCIENTIST}
		\vspace{2px}
	\end{minipage}
	}
	\hspace{0.015\textwidth}
	\begin{minipage}[t]{0.525\textwidth}
		\vspace{3px}
		Equipped with a unique set of skills from experience in industry and academia, I want to pursue research in computer vision to make autonomous cars navigate safely through cities.
		
		\vskip 8px
		{\color{darkgray}\href{mailto:davidstutz@web.de}{\texttt{davidstutz@web.de}} -- \href{http://www.davidstutz.de}{\texttt{davidstutz.de}}}
	\end{minipage}
	
	\vskip 12px
	
	\begin{minipage}[t]{0.435\textwidth}
		{\Large{EDUCATION}}\\[6px]
		\textbf{RWTH Aachen University}\\
		M.Sc., Computer Science (GPA: 1.0)\\
		B.Sc., Computer Science (with Distinction, GPA: 1.1)\\
		{\small\color{darkgray}\textit{Thesis: ``Superpixel Segmentation using Depth Information''\\Advisor: Prof. Dr. Bastian Leibe}}\\
		{\footnotesize\color{lightgray} 10/2011 -- today, Aachen, GER}
		\vskip 6px
		
		\textbf{Georgia Institute of Technology}\\
		Graduate Exchange Student (GPA: 4.0)\\
		{\footnotesize\color{lightgray} 01/2015 -- 05/2015, Atlanta, GA}
		\vskip 8px
		
		{\large{AWARDS}}\\[4px]
		Accenture Future Technology Leaders {\footnotesize\color{lightgray} 2015 -- today}\\
		Hans Hermann-Voss Scholarship {\footnotesize\color{lightgray} 2015}\\
		Germany Scholarship {\footnotesize\color{lightgray} 2014 -- today}\\
		RWTH Aachen University Dean's List {\footnotesize\color{lightgray} 2012, 2013, 2014}\\
		careerloft.de Online Scholarship {\footnotesize\color{lightgray} 2012 -- today}\\
		e-fellows.net Online Scholarship {\footnotesize\color{lightgray} 2011 -- today}\\
		German Physical Society Book Price {\footnotesize\color{lightgray} 2011}
		%German Junior Academy {\footnotesize  2005}
		\vskip 8px
		
		{\large{ONLINE COURSES}}\\[4px]
		{\textbf{Coursera}}\\
		{\small\color{darkgray}\textit{Digital Image and Video Processing,
			Linear and Integer Programming,
			Control of Mobile Robots,
			Natural Language Processing,
			Social Network Analysis,
			Game Theory,
			Cryptography,
			Introduction to Finance
		}}
		\vskip 12px
		
		{\Large{PUBLICATIONS}}\\[6px]
		\vspace{-20px}
		\begingroup
		\renewcommand{\section}[2]{}%
		\begin{thebibliography}{1}
			\bibitem{gcpr}
			D. Stutz.
			\emph{Superpixel Segmentation: An Evaluation}.
			GCPR, 2015.
		\end{thebibliography}
		\endgroup
		\vskip 2px
		
		{\Large{PROJECTS}}\\[6px]
		{See \href{https://www.github.com/davidstutz}{\texttt{github.com/davidstutz}} and \href{http://www.davidstutz.de}{davidstutz.de}}.
		\vskip 6px
		
		Computer Vision\\
		{\small\color{darkgray}\textit{Source code of my thesis, including several superpixel algorithms and the used benchmark; implementations of graph-based image and video segmentation and iPiano for non-convex and non-smooth optimization.}}
		\vskip 6px
		
		Courses and Academia\\
		{\small\color{darkgray}\textit{Publications, thesis, seminar papers and slides, course exercises and course projects.}}
		\vskip 6px
		
		Web Development\\
		{\small\color{darkgray}\textit{Plugins and themes for the frontend framework Twitter Bootstrap, the content management systems Wordpress and CMSimle and the MVC framework Kohana.}}
		\vskip 12px
		
		{\Large{SKILLS}}\\[6px]
		C++ (OpenCV, Boost), Python (OpenCV, Caffe), MatLab, LaTeX (PGFPlots, TikZ), PHP, JavaScript (jQuery, d3.js), SQL, HTML/CSS
		%Microsoft Windows \& Office, Ubuntu, Git
		
		\footnotetext{\scriptsize Grades given in their original grading systems. References upon request.}
		\footnotetext{\scriptsize Last updated: \today.}
	\end{minipage}
	\hspace{0.025\textwidth}
	\begin{minipage}[t]{0.525\textwidth}
		{\Large{EXPERIENCE}}\\[6px]
		\textbf{Microsoft Ireland Research Limited}\\
		Software Engineering Intern\\
		{\small\color{darkgray}\textit{In the Office Marketplace Experience Team, I worked on Centralized Deployment allowing administrators to distribute Office Add-Ins within organizations. The experience improved my software engineering and communication skills and taught me to continuously reflect and learn.}}\\
		{\footnotesize\color{lightgray} 07/2016 -- 09/2016, Dublin, IRL}
		\vskip 6px
		
		\textbf{MOBIS Parts Europe N.V.}\\
		Front Camera Intern\\
		{\small\color{darkgray}\textit{Development of an experimental prototype to evaluate deep learning techniques for pedestrian detection. I got first-hand insights on advanced driver assistance systems, their requirements and the problems faced during development.}}\\
		{\footnotesize\color{lightgray} 04/2016 -- 06/2016, Frankfurt am Main, GER}
		\vskip 6px
		
		\textbf{Computer Vision Group, RWTH Aachen University}\\
		Student Research Assistant\\
		{\small\color{darkgray}\textit{Starting with the results from my bachelor thesis, published at GCPR 2015 \cite{gcpr}, I worked towards a more comprehensive comparison of recent superpixel algorithms. I improved my academic writing and presentation skills and learned to value reproducible research.}}\\
		{\footnotesize\color{lightgray} 05/2015 -- 03/2016, Aachen, GER}
		\vskip 6px
		
		\textbf{Fyusion Inc.}\\
		Research Scientist\\
		{\small\color{darkgray}\textit{I developed experimental prototypes tackling various computer vision problems including line segment and keypoint tracking, statistical clustering and pedestrian detection. By working from home, I learned to communicate results and problems effectively and self-organize my work.}}\\
		{\footnotesize\color{lightgray} 05/2015 -- 03/2016, San Francisco, CA}
		\vskip 6px
		
		\textbf{MATHCCES, RWTH Aachen University}\\
		Tutor, ``Calculus'' and ``Mathematical Foundations II''\\
		{\small\color{darkgray}\textit{Responsible for 30-50 students, I presented weekly exercises, graded homework and final exams, and acted as contact person. This experience improved my mathematical understanding as well as communication and presentation skills.}}\\
		{\footnotesize\color{lightgray} 10/2013 -- 01/2014, 04/2014 -- 09/2014, Aachen, GER}
		\vskip 6px
		
		\textbf{RS Computer GmbH \& Co. KG}\\
		Web Developer\\
		{\small\color{darkgray}\textit{I worked on projects including plugin and theme development for content management and e-commerce systems. Additionally, I completed several development projects for medium-sized companies. This greatly benefited my project management skills.}}\\
		{\footnotesize\color{lightgray} 01/2009 -- 03/2014, 10/2014 -- 04/2015, 10/2016 -- today, Sinzig, GER}
		\vskip 6px
		
		\textbf{Fraunhofer FKIE}\\
		Student Employee\\
		{\small\color{darkgray}\textit{Working on user interfaces for web analytics, including data querying and visualization, this work had major influence on my decision to pursue computer science and taught me proper programming, software engineering and foundations of databases.}}\\
		{\footnotesize\color{lightgray} 10/2009, 05/2011 -- 07/2011, 03/2012, 08/2012 -- 09/2012, Wachtberg, GER}
		
		\vskip 18px
		\begin{minipage}[b]{1\textwidth}\begin{flushright}
		{\color{lightgray}David Stutz}\hskip 6px\fcolorbox{lightgray}{white}{\hphantom{David Stutzaaa}\vphantom{\LARGE David Stutzjgq}}\end{flushright}
		\end{minipage}
	\end{minipage}
}
\end{document}